Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-28 Paper/MSRChallenge2017.tex
added statistical significance to the percentages

The decision tree results suggested that core team members are
important to classifying build success, and thus we investigated the question
directly. 
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set
and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
members are more
likely to have a successful build integration than non-core team members. We hypothesize the reason for this to be that core team members are more familiar with the code, therefore are more likely to have their builds pass.

@@

We also investigated whether developers with followers were more likely to have a
successful build integration, since followers may be seen as ``vouching'' for
the developer's abilities.  We therefore investigated the relationship between
follower count and build success rate (on the data without 
downsampling).  We first investigated whether developers with one or more followers
were more likely to pass the build than those without any followers by
removing commits without any author profile
information (20374 builds, reducing the total build count to
350834). Only 0.87\% (3059/350834) of the
contributions in the data set were performed by developers with zero 
followers.  %, leaving 99.13\% (347775/350834) of the contributions 
%performed by developers with at least one follower.
Developers with 0 followers had a successful build commit 68.49\% (2095/3059)
of the time.  Developers with one or more followers were successful 74.78\%
(260056/347775) of the time.
%
By contrast, developers with a large number of followers (1000 or more),
performed 6.94\% (24347/350834) of the contributions in the 
data set; their
contributions had a 78.61\% (19138/24347) success rate.

>>>>

The decision tree results suggested that core team members are
important to classifying build success, and thus we investigated the question
directly. 
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set
and 64.70\% (25479/39381) of the builds passed.  The p-value from a Fisherexact
test 0.0000, which means that this difference is extremely unlikely to occur by
chance. These results show core team 
members are more
likely to have a successful build integration than non-core team members. We hypothesize the reason for this to be that core team members are more familiar with the code, therefore are more likely to have their builds pass.

@@

We also investigated whether developers with followers were more likely to have a
successful build integration, since followers may be seen as ``vouching'' for
the developer's abilities.  We therefore investigated the relationship between
follower count and build success rate (on the data without 
downsampling).  We first investigated whether developers with one or more followers
were more likely to pass the build than those without any followers by
removing commits without any author profile
information (20374 builds, reducing the total build count to
350834). Only 0.87\% (3059/350834) of the
contributions in the data set were performed by developers with zero 
followers.  %, leaving 99.13\% (347775/350834) of the contributions 
%performed by developers with at least one follower.
Developers with 0 followers had a successful build commit 68.49\% (2095/3059)
of the time.  Developers with one or more followers were successful 74.78\%
(260056/347775) of the time.  The p-value of this difference, calculated with a
Fisher exact test, is 0.000.  This shows commit success difference between
developers with no followers and developers with at least one follower is
very unlikely to occur by chance.
%
By contrast, developers with a large number of followers (1000 or more),
performed 6.94\% (24347/350834) of the contributions in the 
data set; their
contributions had a 78.61\% (19138/24347) success rate. The p-value calculated
by comparing this success rate to the success rate of developers with no
followers is 0.0000.  The p-value means that that the difference between
developers with 1000 followers and developers with no followers is very unlikely
to occur by chance.
